---
title: "p8105_hw2_qs2261"
author: "Qinting Shen"
date: "2023-10-04"
output: github_document
---

```{r, set up}
library(readxl)
library(tidyverse)
```

## Problem 2

read and clean the "Mr. Trash Wheel" sheet, and calculate `homes_powered`

```{r}
mr_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 1, range = "A2:N586", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Mr. Trash"),
         homes_powered = (weight_tons * 500) / 30)
```


read and clean the "Professor Trash Wheel" sheet, and calculate `homes_powered`

```{r}
prof_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 2, range = "A2:M108", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Professor Trash"),
         homes_powered = (weight_tons * 500) / 30)

```


read and clean the "Gwynnda Trash Wheel" sheet, and calculate `homes_powered`

```{r}
gwy_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 4, range = "A2:L157", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Gwynnda Trash"),
         homes_powered = (weight_tons * 500) / 30)

```

combine datasets

```{r}
combine_df=
  bind_rows(mr_df, prof_df, gwy_df) |> 
  select(wheel_type, dumpster, everything())
```

* There are `r nrow(combine_df)` observations and `r ncol(combine_df)` columns in the combined dataset, including `wheel_type`, `dumpster`, `month`, `year`, `date`, `weight_tons`, `volume_cubic_yard`, `plastic_bottles`, `polystyrene`, `cigarette_butts`, `glass_bottles`, `plastic_bags`, `wrappers`, `sports_balls`, and `home_powered`.

* Total weight of trash collected by Professor Trash Wheel is `r sum(prof_df$weight_tons)`.

* Total number of cigarette butts collected by Gwynnda in July of 2021 is 
`r cig=gwy_df |> filter(year=="2021") |> filter(month=="July") sum(pull(cig, cigarette_butts))` 

## Problem 3

Import, clean, and tidy the dataset of baseline demographics.

```{r}
mci_baseline_df=
  read_csv("data/data_mci/MCI_baseline.csv", skip = 1) |> 
  janitor::clean_names() |> 
  mutate(sex=recode(sex, "1" = "male", "0" = "female")) |> 
  mutate(apoe4=recode(apoe4, "1" = "APOE4 carrier", "0" = "APOE4 non-carrier")) |> filter(age_at_onset !=".") |> 
  mutate(age_at_onset= as.numeric(age_at_onset))
```

I recoded the sex and apoe4 variables to make it easier for people to understand the meaning, and select those who have MCI into our dataset, and then change the `age_at_onset` variable to numeric variable.

* I recruited `r nrow(mci_baseline_df)` participants
`r mci_baseline_df |> filter(`


import, clean, and tidy the dataset of longitudinally observed biomarker values

```{r}
mci_amyloid_df=
  read_csv("data/data_mci/mci_amyloid.csv", skip=1) |> 
  janitor::clean_names() |> 
  rename(id=study_id, time_0= baseline) |> 
  mutate(time_0 = as.numeric(time_0), time_2 = as.numeric(time_2), time_4 = as.numeric(time_4), time_6 = as.numeric(time_6), time_8 = as.numeric(time_8)) |> pivot_longer(time_0:time_8, names_to = "years_elapsed_since_baseline", values_to = "amyloid_42_40_ratio", names_prefix = "time_")
```

I changed the data name into the right format, and rename the `study_id` and `baseline` to make them match the variable name in baseline dataset. And then I change the time variables to numeric type, and modify the time variable to avoid them being to long.
