---
title: "p8105_hw2_qs2261"
author: "Qinting Shen"
date: "2023-10-04"
output: github_document
---

```{r, set up}
library(readxl)
library(tidyverse)
```

## Problem 2

read and clean the "Mr. Trash Wheel" sheet, and calculate `homes_powered`

```{r}
mr_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 1, range = "A2:N586", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Mr. Trash"),
         homes_powered = (weight_tons * 500) / 30)
```


read and clean the "Professor Trash Wheel" sheet, and calculate `homes_powered`

```{r}
prof_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 2, range = "A2:M108", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Professor Trash"),
         homes_powered = (weight_tons * 500) / 30)

```


read and clean the "Gwynnda Trash Wheel" sheet, and calculate `homes_powered`

```{r}
gwy_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 4, range = "A2:L157", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Gwynnda Trash"),
         homes_powered = (weight_tons * 500) / 30)

```

combine datasets

```{r}
combine_df=
  bind_rows(mr_df, prof_df, gwy_df) |> 
  select(wheel_type, dumpster, everything())
```

* There are `r nrow(combine_df)` observations and `r ncol(combine_df)` columns in the combined dataset, including `wheel_type`, `dumpster`, `month`, `year`, `date`, `weight_tons`, `volume_cubic_yard`, `plastic_bottles`, `polystyrene`, `cigarette_butts`, `glass_bottles`, `plastic_bags`, `wrappers`, `sports_balls`, and `home_powered`.

* Total weight of trash collected by Professor Trash Wheel is `r sum(prof_df$weight_tons)`.

* Total number of cigarette butts collected by Gwynnda in July of 2021 is 
`r cig=gwy_df |> filter(year=="2021") |> filter(month=="July") sum(pull(cig, cigarette_butts))` 

## Problem 3

Import, clean, and tidy the dataset of baseline demographics.

```{r}
mci_baseline_df=
  read_csv("data/data_mci/MCI_baseline.csv", skip = 1) |> 
  janitor::clean_names() |> 
  mutate(sex=recode(sex, "1" = "male", "0" = "female")) |> 
  mutate(apoe4=recode(apoe4, "1" = "APOE4 carrier", "0" = "APOE4 non-carrier")) |> filter(age_at_onset !=".") |> 
  mutate(age_at_onset= as.numeric(age_at_onset))
```



