---
title: "p8105_hw2_qs2261"
author: "Qinting Shen"
date: "2023-10-04"
output: github_document
---

```{r, set up}
library(readxl)
library(tidyverse)
```

## Problem 2

read and clean the "Mr. Trash Wheel" sheet, and calculate `homes_powered`

```{r}
mr_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 1, range = "A2:N586", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Mr. Trash"),
         homes_powered = weight_tons * 500 / 30)
```


read and clean the "Professor Trash Wheel" sheet, and calculate `homes_powered`

```{r}
prof_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 2, range = "A2:M108", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Professor Trash"),
         homes_powered = weight_tons * 500 / 30)

```


read and clean the "Gwynnda Trash Wheel" sheet, and calculate `homes_powered`

```{r}
gwy_df=read_excel("data/202309 Trash Wheel Collection Data (1).xlsx", sheet = 4, range = "A2:L157", col_names = TRUE) |> 
  janitor::clean_names() |> 
  mutate(year=as.numeric(year),
         wheel_type=c("Gwynnda Trash"),
         homes_powered = weight_tons * 500 / 30)

```

combine datasets

```{r}
combine_df=
  bind_rows(mr_df, prof_df, gwy_df) |> 
  select(wheel_type, dumpster, everything())
```


* Write a paragraph about these data; you are encouraged to use inline R. Be sure to note the number of observations in the resulting dataset, and give examples of key variables. For available data, what was the total weight of trash collected by Professor Trash Wheel? What was the total number of cigarette butts collected by Gwynnda in July of 2021?

* There are `r nrow(combine_df)` observations in the combined dataset, including `wheel_type`, `dumpster`, `month`, `year`, `date`, `weight_tons`, `volume_cubic_yard`, `plastic_bottles`, `polystyrene`, `cigarette_butts`, `glass_bottles`, `plastic_bags`, `wrappers`, `sports_balls`, and `home_powered`.

* Total weight of trash collected by Professor Trash Wheel is `r sum(prof_df$weight_tons)`.

* Total number of cigarette butts collected by Gwynnda in July of 2021 is 
`r sum((gwy_df, year == 2021 & month == "July")$cigarette_butts)` 



